---
title: "Definitions"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, messages=TRUE, error=TRUE)
```


##Functions 



###General 

1. help(topic) 
   Opens up the topic in the R-help tab and describes the functions and the arguments used for it 
```{r}
help("mode")
```
  
2. ?topic 
   This function does the same as help(topic): opens the R-help tab and describes the functions and the arguments used for it 
```{r}
?mean
```
   
3. ls() 
   Lists what objects are currently in your R environment 
```{r}
ls()
```
  
4. dir() 
   Lists the names of each file in your R project 
```{r}
dir()
```
   
5. list.files() 
   This function does the same as dir(): lists the names of each file in your R project 
```{r}
list.files()
```
   
###Input and Output 

1. save()
   Saves an R object to a specific file 
```{r}
a <- 1
save("a", file="file1.txt")
```
   
2. load() 
   Loads saved data 
```{r}
load(file="file1.txt")
```
   
3. data() 
   Loads specific data 
```{r}
data("NationalCensus")
```
   
4. library() 
   Loads a library or a package into R 
```{r}
library(psych)
```
   
5. read.table()
   Reads a table and produces the data frame 
```{r}
read.table(file="file1.txt")
```
   
6. read.csv() 
   This function is the same as read.table(): It reads a table and produces the data frame 
```{r}
read.csv(file="file1.txt")
```
   
7. scan()
   Reads data into a vector from a console or file 
```{r}
scan(file="file1.txt")
```
   
8. print()
   Prints the contents 
```{r}
print("class")
```
   
9. cat()
   Concatenates the data and prints the contents 
```{r}
cat("class","assignment")
```

10. write.table() 
    Converts the contents to a data frame and prints it 
```{r}
write.table(x, file="file1.txt")
```
    
### Data Creation 

1. c() 
   Combines data into a vector 
```{r}
c(1,2,3)
```
   
2. from:to (where from and to are replaced with numbers, e.g. 1:10) 
   Lists all numbers in between the given numbers 
```{r}
1:10
```
   
3. seq()
   Lists numbers from the first argument to the second argument, adding the third argument to the first argument until the third argument is reached.
```{r}
seq(1, 10, 3)
```

4. rep() 
   Replicates the values in the first argument for the amount of times indicated in the second argument 
```{r}
rep(4,8)
```
   
5. data.frame()
   Creates data frames 
```{r}
data.frame()
```
   
6. list() 
   Checks for different kinds of lists (generic and dotted pairs) in R 
```{r}
lists()
```
   
7. matrix() 
   Creates a matrix 
```{r}
x <- (1:5)
matrix(x)
```
   
8. factor() 
   
   
   
   
   
   

```{r}
?factor
```



