---
title: "R Basics"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

### Problem 1 

Do simple math with numbers, addition, subtraction, multiplication, division 

```{r eval=false}
1+1
3-2
4*6
5/7
```
### Problem 2

Put numbers into variables, do simple math on the variables 

```{r eval=false}

marsha <- 1
abc <- 8745416786468465646

marsha + abc 


cats <- 476 
dogs <- 8.3 

cats / dogs 

class <- 33 
teacher <- 87 

class - teacher 

high <- 10246839295 
low <- 376782853 

high * low 
```

### Problem 3 

Write code that will place the numbers 1 to 100 separately into a variable using for loop. Then, again using the seq function.

```{r eval=false}
for(i in 1:100){ 
  print(i)
} 

seq(1,100)

```

### Problem 4 

Find the sum of all the integer numbers from 1 to 100. 

```{r eval=false}

sum(seq(1,100))

```

How would you do this without using the sum function? For example, how could you use a for loop to accomplish this task?

```{r eval=false}
totalsum<-0
for(i in 1:100){
  totalsum<-c(totalsum+i)
}
print(totalsum)
```

### Problem 5 

Write a function to find the sum of all integers between any two values. 

```{r eval=false}

x<-c(5:250)

SumFun<-function(y){
  sum<-0
  for(i in 1:length(y)){
    sum=sum+y[i]
  }
print(sum)
}
SumFun(x)
```

### Problem 6 

List all of the odd numbers from 1 to 100. 

```{r eval=false}

AllNumbers<-c()
for(i in 1:100){
  AllNumbers<-c(AllNumbers,i)
}
OddNumbers<-c()
for (x in AllNumbers)
  if(x%%2 ==1){
    OddNumbers<-c(OddNumbers,x)
    
  }
print(OddNumbers)
```

### Problem 7 

List all of the prime numbers from 1 to 1000. 

```{r eval=false}

n <-c(1:1000)
  PrimeNumbers<-function(n){
    if(n==2){
      TRUE
    } else if (any(n%%2:(n-1)==0)){
      FALSE
    } else {
      TRUE
    }
  }
PrimeNumbers <- Vectorize(PrimeNumbers)

n[PrimeNumbers(n)]
```

### Problem 8 

Generate 100 random numbers 

```{r eval=false}

runif(100) 

```

### Problem 9 

Generate 100 random numbers within a specific range 

```{r eval=false}

runif(100, min=0, max=650) 

```

### Problem 10 

Write your own functions to give descriptive statistics for a vector variable storing multiple numbers. Write functions for the following without using R intrinsics: mean, mode, median, range, standard deviation 

Mean:

```{r eval=false}

meanA <- function(m){ 
  AllSum<-0
  for(i in m){
    AllSum <- AllSum+i
  }
return<-c(AllSum/length(m))   
}
mean_numbers<-c(1,5,10,15,20)

print(meanA(mean_numbers)) 
```

Mode: 

```{r eval=false}


```

Median: 

```{r eval=false}

```

Range: 

```{r eval=false}

```

Standard deviaton: 

```{r eval=false}

```

### Problem 11 

Count the number of characters in a string variable 

```{r eval=false}

string_a <- "numberofcharactersinastring"
strsplit(string_a,split="")
```

### Problem 12 

Count the number of words in a string variable 

```{r eval=false}
string_b <- "here is my example sentence that needs to be split up"
strsplit(string_b,split=" ")
```

### Problem 13 

Count the number of sentences in a string variable 

```{r eval=false}

string_c <- "here is my example sentence . it needs to be split up . i do not know what to write . here is the fourth sentence just because"

strsplit(string_c,split=" . ")
```

### Problem 14 

Count the number of times a specific character occurs in a string variable 
```{r eval=false}

string_d <-c(1,4,8,6,3,2,4,6,8,9,6,2,3,6,8,9,5,3,2,3,5,6)
table(string_d)
```

How would you do this without the table function? 

```{r eval=false}

```

### Problem 15 

Do a logical test to see if one word is found within the text of another string variable 

```{r eval=false}

a <- "we"

b <- "we turn on the computer"


# is a in b? 
a%in%b


```

